Parsing medial prefrontal cortex: A joint meta-analytic and graph-theoretic approach.

### 2018-08-24 Manuscript/Manuscript.Rmd
Phrasing and citations

  Studies of decision making have consistently associated activity in vmPFC with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Kable & Glimcher, 2007). However, the distributed cortical valuation system also includes posterior cingulate and other mPFC regions, which collectively show significant spatial overlap with the default mode network along the medial wall (DMN; Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011). This shared neural coverage has prompted the question of whether (and to what extent) these two systems can be dissociated.

@@

  In this study, we aim to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, so that we can more precisely describe the network's features (i.e. stability, expanse) and generate more informed topographic targets for future studies of decision making. We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data. First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature projected to an established brain atlas (Glasser et al., 2013). We then produce a rsFC networks of all the surface vertices within these ROIs for each individual resting state dataset from the Human Connectome Project, and estimate the extent of DMN coverage through community detection. The resulting partitions are then evaluated for consistency across methods, throughout each individual's time series, and across subjects.

@@

>>>>

  Studies of decision making have consistently associated activity in vmPFC with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Hiser & Koenigs, 2017; Kable & Glimcher, 2007; Levy et al., 2011). However, the distributed cortical valuation system also includes posterior cingulate and other mPFC regions, which collectively show significant spatial overlap with the default mode network along the medial wall (DMN; Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011). This shared neural coverage has prompted the question of whether (and to what extent) these two systems can be dissociated.

@@

  In this study, we aim to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, quantifying the degree of topographical heterogeneity present in this network within and across individuals. This description will allow researchers to generate more precise topographic targets for future studies of decision making. We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data. First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature projected to an established brain atlas (Glasser et al., 2013). We then produce a rsFC networks of all the surface vertices within these ROIs for each individual resting state dataset from the Human Connectome Project, and estimate the extent of DMN coverage through community detection. The resulting partitions are then evaluated for consistency across methods, throughout each individual's time series, and across subjects.

@@

Gratton et al. (2018) have figures similar to ours indicating within subject stability being higher than across-subject similarity (3A). Our twist would be that we are quantifying a finer resolution level restricted to the ROIs (they use a 333 region parcellation), and they estimated it for the MSC only.9 So: what they find persists when examined at a finer level of resolution for a widespread sample.
